Tropical Andes plant trait data TRY

### 2023-12-06 code/L0/L0_TropicalAndes_plants_TRY.Rmd
Add keep only records with non-NA trait IDs

# Load required packages
```{r}
library(rtry)
library(dplyr)
```

@@

@@

>>>>

# Load required packages
```{r}
library(rtry)
library(dplyr)
library(tidyr)
```

@@

# Keep only record with non-NA trait IDs
```{r}
try_data <- try_data %>%
  drop_na(TraitID)
nrow(try_data)
```

@@

# Get units for each trait
```{r}
try_data %>% distinct(TraitName, UnitName)
```
